Predicting children's and adults' preferences in physical interactions via physics simulation

### 2021-05-12 paper/paper2021.Rmd
finalized CogSci 2021 revisions

author-information: > 
    \author{
    {\large \bf George Kachergis}$^{1,\star}$, {\large \bf Samaher Radwan}$^1$, {\large \bf Bria Long}$^1$,  
    {\large \bf Judith Fan}$^2$, \\
    {\large \bf Daniel Bear}$^{1,3}$, {\large \bf Daniel Yamins}$^{1,3}$, \and {\large \bf Michael C.~Frank}$^1$ \\ 
    $^1$Department of Psychology, Stanford University \\
    $^2$Department of Psychology, University of California at San Diego \\
    $^3$Department of Computer Science, Stanford University \\
    $^{\star}$\texttt{kachergis@stanford.edu}}

>>>>

author-information: > 
    \author{
    {\large \bf George Kachergis}$^{1,\star}$, {\large \bf Samaher Radwan}$^1$, {\large \bf Bria Long}$^1$,  
    {\large \bf Judith Fan}$^2$, \\
    {\large \bf Michael Lingelbach}$^{1,3}$, {\large \bf Daniel M. Bear}$^{1,3}$, {\large \bf Daniel L. K. Yamins}$^{1,3}$, \and {\large \bf Michael C.~Frank}$^1$ \\ 
    $^1$Department of Psychology, Stanford University \\
    $^2$Department of Psychology, University of California at San Diego \\
    $^3$Department of Computer Science, Stanford University \\
    $^{\star}$\texttt{kachergis@stanford.edu}}
